Variable creation ObjectInAction

### 2019-04-25 Final Manuscript.Rmd
results

```{r setup, include = FALSE}
library(papaja)
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
library(apaTables)

clark_measures <- read.csv("Cleaned data/clark_measures.csv")
smith <- read.csv("Cleaned data/smith.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
```

@@

@@

>>>>

```{r setup, include = FALSE}
library(papaja)
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
library(apaTables)
library(knitr)
library(kutils)
library(tidyverse)
library(lavaan)
library(xtable)
clark_measures <- read.csv("Cleaned data/clark_measures.csv")
smith <- read.csv("Cleaned data/smith.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
```

@@

## Analysis Strategy
In Figure\ \@ref(fig:semfigure)

##Main Results
All model estimates and p-values are found in Table\ \@ref(tab:sem). The most important findings from @garcia2016objectification were the significant partner effect between actor SSO and partner objectification (specifically men's objectification of women and women's SSO), and the link between actor SSO and actor authenticity (also specifically for women). We did not find a significant effect between actor SSO and actor authenticity ($\beta$= -.10, $p$=.38), which means we do not have evidence to support the idea that partner objectification is the cause for the negative effects related to relationship inauthenticity. However, we did find a significant relationship between partner objectification and actor SSO ($\beta$= .25, $p$=.03), which supports our hypothesis that objectification from other women also causes women to self-objectify just as it does in interactions between male-female pairs. We also found a significantly negative effect of authenticity on career aspirations ($\beta$= .18, $p$=.01) and relationship agency ($\beta$=.27, $p$=.01). We found that the model had good fit.

@@

```{r, include=FALSE}
#Filtering for just one partnum and creating TSO * objectification interaction
dyad_cswomen <- clarksmith_women %>%
  mutate(TSO_P_SOO_A = TSO_P*a2pSOO_A,
         TSO_A_SOO_P = TSO_A*a2pSOO_P) %>%
  filter(partnum_A==1)

model <- '#####regressions 
howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P + c*TSO_A_SOO_P
authenticity_A ~ d*howbody_avg_A
howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A + c*TSO_P_SOO_A
authenticity_P ~ d*howbody_avg_P
trigram_score_A ~ e1*authenticity_A
careerasp_A ~ e2*authenticity_A
relag_A ~ e3*authenticity_A
trigram_score_P ~ e1*authenticity_P
careerasp_P ~ e2*authenticity_P
relag_P ~ e3*authenticity_P
######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
trigram_score_A ~~ trigram_score_P
careerasp_A ~~ careerasp_P
relag_A ~~ relag_P
trigram_score_A ~~ 0*careerasp_A
trigram_score_A ~~ 0*relag_A
trigram_score_A ~~ 0*careerasp_P
trigram_score_A ~~ 0*relag_P
careerasp_A ~~ 0*relag_A
careerasp_A ~~ 0*trigram_score_P
careerasp_A ~~ 0*relag_P
relag_A ~~ 0*trigram_score_P
relag_A ~~ 0*careerasp_P
trigram_score_P ~~ 0*careerasp_P
trigram_score_P ~~ 0*relag_P
careerasp_P ~~ 0*relag_P
#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
TSO_A_SOO_P ~~ c5*a2pSOO_A
TSO_P_SOO_A ~~ c5*a2pSOO_P
TSO_A_SOO_P ~~ c6*TSO_P
TSO_P_SOO_A ~~ c6*TSO_A
'

isatmodel <- '#####regressions 
#Part one/two
howbody_avg_A ~~ t*TSO_A
howbody_avg_A ~~ a*a2pSOO_A
howbody_avg_A ~~ b*a2pSOO_P 
howbody_avg_A ~~ c*TSO_A_SOO_P

howbody_avg_P ~~ t*TSO_P
howbody_avg_P ~~ a*a2pSOO_P 
howbody_avg_P ~~ b*a2pSOO_A 
howbody_avg_P ~~ c*TSO_P_SOO_A

TSO_A ~~ f*howbody_avg_P
TSO_P ~~ f*howbody_avg_A
TSO_A_SOO_P ~~ g*howbody_avg_P
TSO_P_SOO_A ~~ g*howbody_avg_A

#Part two/three
authenticity_A ~~ d*howbody_avg_A
authenticity_P ~~ d*howbody_avg_P
howbody_avg_A ~~ h*authenticity_P
howbody_avg_P ~~ h*authenticity_A

#Part three/four
trigram_score_A ~~ e1*authenticity_A
trigram_score_P ~~ e1*authenticity_P
careerasp_A ~~ e2*authenticity_A
careerasp_P ~~ e2*authenticity_P
relag_A ~~ e3*authenticity_A
relag_P ~~ e3*authenticity_P
trigram_score_A ~~ e4*relag_P
trigram_score_P ~~ e4*relag_A
trigram_score_A ~~ e5*careerasp_P
trigram_score_P ~~ e5*careerasp_A
trigram_score_A ~~ e6*trigram_score_P
#trigram_score_P ~~ e6*trigram_score_A
careerasp_A ~~ e7*relag_P
careerasp_P ~~ e7*relag_A
careerasp_A ~~ e8*careerasp_P
#careerasp_A ~~ e9*trigram_score_P
#careerasp_P ~~ e9*trigram_score_A
relag_A ~~ e10*relag_P

#One to three
#direct actor effects
authenticity_A ~~ k1*TSO_A_SOO_P
authenticity_P ~~ k1*TSO_P_SOO_A
authenticity_A ~~ k2*TSO_A
authenticity_P ~~ k2*TSO_P
authenticity_A ~~k3*a2pSOO_A
authenticity_P ~~k3*a2pSOO_P

#direct partner effects
authenticity_A ~~ k4*TSO_P_SOO_A
authenticity_P ~~k4*TSO_A_SOO_P
authenticity_A ~~ k5*TSO_P
authenticity_P ~~ k5*TSO_A
authenticity_A ~~ k6*a2pSOO_P
authenticity_P ~~ k6*a2pSOO_A

#One to four
#Direct actor effects
trigram_score_A ~~ l1*TSO_A_SOO_P
trigram_score_P ~~ l1*TSO_P_SOO_A
trigram_score_A ~~ l2*TSO_A
trigram_score_P ~~ l2*TSO_P
trigram_score_A ~~ l3*a2pSOO_A
trigram_score_P ~~ l3*a2pSOO_P
careerasp_A ~~ l4*TSO_A_SOO_P
careerasp_P ~~ l4*TSO_P_SOO_A
careerasp_A ~~ l5*TSO_A
careerasp_P ~~ l5*TSO_P
careerasp_A ~~ l6*a2pSOO_A
careerasp_P ~~ l6*a2pSOO_P
relag_A ~~ l7*TSO_A_SOO_P
relag_P ~~ l7*TSO_P_SOO_A
relag_A ~~ l8*TSO_A
relag_P ~~ l8*TSO_P
relag_A ~~ l9*a2pSOO_A
relag_P ~~ l9*a2pSOO_P

#direct partner effects
trigram_score_A ~~ m1*TSO_P_SOO_A
trigram_score_P ~~ m1*TSO_A_SOO_P
trigram_score_A ~~ m2*TSO_P
trigram_score_P ~~ m2*TSO_A
trigram_score_A ~~ m3*a2pSOO_P
trigram_score_P ~~ m3*a2pSOO_A
careerasp_A ~~ m4*TSO_P_SOO_A
careerasp_P ~~ m4*TSO_A_SOO_P
careerasp_A ~~ m5*TSO_P
careerasp_P ~~ m5*TSO_A
careerasp_A ~~ m6*a2pSOO_P
careerasp_P ~~ m6*a2pSOO_A
relag_A ~~ m7*TSO_P_SOO_A
relag_P ~~ m7*TSO_A_SOO_P
relag_A ~~ m8*TSO_P
relag_P ~~ m8*TSO_A
relag_A ~~ m9*a2pSOO_P
relag_P ~~ m9*a2pSOO_A

#Two to four
#direct actor effects
trigram_score_A ~~ o1*howbody_avg_A
trigram_score_P ~~ o1*howbody_avg_P
careerasp_A ~~ o2*howbody_avg_A
careerasp_P ~~ o2*howbody_avg_P
relag_A ~~ o3*howbody_avg_A
relag_P ~~ o3*howbody_avg_P

#direct partner effects
trigram_score_A ~~ o1*howbody_avg_P
trigram_score_P ~~ o1*howbody_avg_A
careerasp_A ~~ o2*howbody_avg_P
careerasp_P ~~ o2*howbody_avg_A
relag_A ~~ o3*howbody_avg_P
relag_P ~~ o3*howbody_avg_A

######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
#trigram_score_A ~~ trigram_score_P
#careerasp_A ~~ careerasp_P
#relag_A ~~ relag_P
trigram_score_A ~~ q1*careerasp_A 
trigram_score_A ~~ q2*relag_A

careerasp_A ~~ q3*relag_A

trigram_score_P ~~ q1*careerasp_P
trigram_score_P ~~ q2*relag_P

careerasp_P ~~ q3*relag_P

trigram_score_A ~~ q4*careerasp_P
trigram_score_A ~~ q5*relag_P

trigram_score_P ~~ q4*careerasp_A
trigram_score_P ~~ q5*relag_A

careerasp_A ~~ q6*relag_P
careerasp_P ~~ q6*relag_A

#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
TSO_A_SOO_P ~~ c5*a2pSOO_A
TSO_P_SOO_A ~~ c5*a2pSOO_P
TSO_A_SOO_P ~~ c6*TSO_P
TSO_P_SOO_A ~~ c6*TSO_A
'

fit <- sem(model, data=dyad_cswomen)
```

```{r sem, include=TRUE, results='asis'}
fit_table <- xtable(parameterEstimates(fit))

fit_table <- fit_table %>%
  filter(op=="~") %>%
  mutate(lhs = ifelse(lhs == "howbody_avg_A", "Actor SSO", 
                      ifelse(lhs=="authenticity_A", "Actor Authenticity",
                             ifelse(lhs=="howbody_avg_P", "Partner SSO",
                                    ifelse(lhs=="authenticity_P", "Partner Authenticity", 
                                           ifelse(lhs=="relag_A", "Actor Rel. Agency",
                                                  ifelse(lhs=="relag_P", "Partner Rel. Agency",
                                                         ifelse(lhs=="careerasp_A", "Actor Career Aspirations",
                                                                ifelse(lhs=="careerasp_P", "Partner Career Aspirations",
                                                                       ifelse(lhs=="trigram_score_A", "Actor Cog. Performance",
                                                                              ifelse(lhs=="trigram_score_P", "Partner Cog. Performance", NA)))))))))),
         rhs = ifelse(rhs=="TSO_A", "Actor TSO",
                      ifelse(rhs=="a2pSOO_A", "Actor Obj. of Partner",
                             ifelse(rhs=="a2pSOO_P", "Partner Obj. of Actor",
                                    ifelse(rhs=="TSO_A_SOO_P", "Actor TSO x Partner Obj.",
                                           ifelse(rhs == "howbody_avg_A", "Actor SSO",
                                                  ifelse(rhs=="howbody_avg_P", "Partner SSO",
                                                         ifelse(rhs=="TSO_P", "Partner TSO",
                                                                ifelse(rhs=="TSO_P_SOO_A", "Partner TSO x Actor Obj.",
                                                                       ifelse(rhs=="authenticity_A", "Actor Authenticity", 
                                                                              ifelse(rhs=="authenticity_P", "Partner Authenticity", NA))))))))))) %>%
  select(lhs, op, rhs, est, se, z, pvalue) %>%
  #taking out partner-partner estimates
  slice(1:5,11:13)

colnames(fit_table) <- c("Path", "", "", "Estimate", "SE", "z-value", "p-value")

apa_table(fit_table, caption = "Estimates from final Path Analysis Model", font_size = "small")
```

```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model with Estimates"}
include_graphics("SEMfigure.png")
```
